### 2014-09-29 Docs/networks/networks.tex
renname docs Docs
add a note about rprox in the networks chapter

\section{Networks}

@@

@@

>>>>

\section{Introduction to \maestro\ Networks}

@@

\section{Notes of Specific Networks}

@@

\subsection{{\tt rprox}}

This is a network introduced in \cite{xrb2} that has 10 species
approximates hit CNO burning, triple-$\alpha$, and rp-process 
breakout up through $^{56}\mathrm{Ni}$.  Updated rates from
ReacLib~\cite{ReacLib} are used.  The overall ideas in this 
network are based on Appendix C of \cite{wallacewoosley:1981}.
